\documentclass{exam}\title{CM30073: ADVANCED ALGORITHMS AND COMPLEXITY}\date{}\examcode{CM30073}\calculators\papertype{PartII}\begin{document}\maketitle\begin{question}\begin{roster}\item[(a)]Explain the purpose of introducing the concepts of {\em Non-deterministic Turing Machine (NTM)}and the complexity class {\em NP}.Illustrate your explanation by two examples of concrete {\bf Yes-No}-problems which lead tothese concepts.\marks{6}\item[(b)]When is an input word said to be {\em accepted} by an NTM?When is a {\bf Yes-No}-problem said to be {\em solved} by an NTM?Give a definition of the {\em complexity} of an NTM.\marks{7}\item[(c)]Define the complexity class {\em co-NP}, and illustrate by an example of a concrete {\bf Yes-No}-problemwhy one might be interested in this concept.Compare $P \neq NP$ and $NP \neq$ {\em co-NP} hypotheses.What can you say about the set $NP \setminus (P \cup NPC)$ (where $NPC$ is the class of all $NP$-completeproblems) under the assumption that $P \neq NP$?\marks{7}\end{roster}\end{question}\begin{question}\begin{roster}\item[(a)]Formulate the {\em $q$-Clique} problem for an undirected graph and the {\em CNF Satisfiability} problem.Prove that {\em $q$-Clique} problem is $NP$-complete using a polynomial transformation to this problem of the{\em CNF Satisfiability} problem (assumed $NP$-complete).\marks{7}\item[(b)]Formulate the ({\bf Yes-No} version of) the {\em Travelling Salesman} problem and the{\em Hamiltonian Cycle} problem.Prove that the {\em Travelling Salesman} problem is $NP$-complete using a polynomial transformation tothis problem of the {\em Hamiltonian Cycle} problem (assumed $NP$-complete).\marks{7}\item[(c)]Prove that the optimization version of the {\em Travelling Salesman} problem is $NP$-hard.\marks{6}\end{roster}\end{question}\begin{question}\begin{roster}\item[(a)]Define the terms ``approximation algorithm with polynomial complexity'' and ``ratio bound''.\marks{4}\item[(b)]Describe an approximation algorithm with polynomial complexity for the optimizationversion of the {\em Travelling Salesman with triangle inequality} problem, using if necessary,some known polynomial complexity algorithms as subroutines.\marks{8}\item[(c)]Does there exist an approximation algorithm with polynomial complexity and a constantratio bound for the standard optimization version of {\em Travelling Salesman}?Justify your answer.\marks{8}\end{roster}\end{question}\begin{question}\begin{roster}\item[(a)]Give a definition of a semialgebraic set in ${\bf R}^n$.Characterize (without giving a proof) semi-decidable sets of Real Numbers machines in terms ofsemialgebraic sets.\marks{3}\item[(b)]Give a definition of the class $NP$ for Real Numbers machines.Describe an example of an $NP$-complete problem in this class (you don't need to {\em prove}$NP$-completeness of this problem).\marks{7}\item[(c)]Prove the lower complexity bound $\Omega(n \log n)$ for sorting-by-comparisons.\marks{7}\item[(d)]Formulate the {\em Distinctness} problem.What is the best lower complexity bound for this problem when using Algebraic Computation Trees?(You don't need to prove this bound.)\marks{3}\end{roster}\end{question}\paperend{NNV/JP}\end{document}